Tables

### 2023-03-08 Semester II/Research Method/Manuskrip ke Software X/Manuscript/table only.Rmd
update baru

>>>>

- tes 1
- tes 2

# Sek 1

## Sek 2

### lalala

__Policy 1__

---

Let:

- $M = \left\{ 1,2,3,4 \right\}$ as the set of weeks on the supply cycle, 
- $N$ as the number of raw materials, 
- $\mathfrak{N}= \left\{ 1,2,...,N \right\}$ as the set of raw-materials,
- $I$ as the number of items,
- $\mathfrak{J} =  \left\{ 1, 2, ..., I  \right\}$ as the number of items,
- $P \bigcup_{j \in M} P_j$ as the set of items to be produced on the planning horizon, where $P_j$ as the set of items to be produced on week $j$.
- For $i \in \mathfrak{J}, k \in \mathfrak{N}$,

$$f_{ik} = 
\left\{\begin{matrix}
1 & , & \text{if item } i \text{ can be produce by using raw material } k  \\ 
0 & , & \text{otherwise}
\end{matrix}\right. 
$$

- lala
